Near Optimal Behavior with Approximate Abstraction

### 2016-02-04 paper/introduction.tex
Intro done for now

\section{Introduction}
Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant. Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction. However, \textit{exact abstractions}, which treat fully-identical situations alike, require complete knowledge that is often computationally intractable to obtain. Furthermore, often no two situations are identical, so exact abstractions are often ineffective. To overcome these issues we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical. This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}. The remainder of our introduction contextualizes these intuitions in \acp{MDP}.

@@

% Thesis: Approximate abstraction for three reasons.
Performing approximate abstraction in \acp{MDP} by relaxing the state aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits. First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}. In contrast, exact abstractions often require solving for optimal behavior, thereby defeating the purpose of abstraction. Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than exact abstractions. This difference is particularly important in environments where no two states are identical. \dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states. The thesis of this work is that aggregation of states on the basis of various approximate criteria can reduce state space size while incurring only bounded error in the resulting behavior.

>>>>

\section{Introduction}
Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant. Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction. However, \textit{exact abstractions}, which treat fully-identical situations as equivalent, require complete knowledge that is often computationally intractable to obtain. Furthermore, often no two situations are identical, so exact abstractions are often ineffective. To overcome these issues we investigate \textit{approximate abstractions} that enable agents to treat sufficiently similar situations as identical. This work characterizes the impact of equating ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}. The remainder of our introduction contextualizes these intuitions in \acp{MDP}.

@@

% Thesis: Approximate abstraction for three reasons.
The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits while maintaining bounded error in the resulting behavior. First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}. In contrast, exact abstractions often require solving for optimal behavior, thereby defeating the purpose of abstraction. Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than exact abstractions. This difference is particularly important in environments where no two states are identical. \dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
